\vspace{5em}On Evaluating Adversarial Robustness

### 2019-02-19 paper.tex
Fix minor typos

To date, most defenses to adversarial examples typically restrict the adversary to
making ``small'' changes to inputs from the data-generating
distribution (e.g. inputs from the test set).
%
Formally, for some natural input $x$ and similarity metric $\
mathcal{D}$, $x'$ is considered a valid adversarial example if
$\mathcal{D}(x, x')\leq \epsilon$ for some small $\epsilon$ and $x'$ is
misclassified\footnote{
  It is often required that the original input $x$ is classified
  correctly, but this requirement can vary across papers.
  Some papers consider $x'$ an adversarial example as long as it
  is classified \emph{differently} from $x$.}.
%
This definition is motivated by the assumption that small changes under
the metric $\mathcal{D}$ do not change the true class of the input and
thus should not cause the classifier to predict an erroneous class.

@@

Nevertheless, such a rigorous and precise definition of the
adversary's capability, leads to well-defined measures of
adversarial robustness that are, in principle, computable.
%
For example, given a model $f(\cdot$, one common way to define
robustness is the worst-case loss $L$ for a given perturbation budget,
\[
\mathop{\mathbb{E}}_{(x,y) \sim \mathcal{X}}\bigg[
  \max_{x' : \mathcal{D}(x,x') < \epsilon} L\big(f(x'),y\big) \bigg].
\]
Another commonly adopted definition is the average (or median)
minimum-distance of the adversarial perturbation,
\[
\mathop{\mathbb{E}}_{(x,y) \sim \mathcal{X}}\bigg[
  \min_{x' \in A_{x,y}} \mathcal{D}(x,x') \bigg],
\]
where $A_{x,y}$ depends on the definition of \emph{adversarial example},
e.g. $A_{x,y} = \{x' \mid f(x') \ne y\}$ for misclassification
or $A_{x,y} = \{x \mid f(x') = t\}$ for some target class $t$.

>>>>

To date, most defenses to adversarial examples typically restrict the adversary to
making ``small'' changes to inputs from the data-generating
distribution (e.g. inputs from the test set).
%
Formally, for some natural input $x$ and similarity metric
$\mathcal{D}$, $x'$ is considered a valid adversarial example if
$\mathcal{D}(x, x')\leq \epsilon$ for some small $\epsilon$ and $x'$ is
misclassified\footnote{
  It is often required that the original input $x$ is classified
  correctly, but this requirement can vary across papers.
  Some papers consider $x'$ an adversarial example as long as it
  is classified \emph{differently} from $x$.}.
%
This definition is motivated by the assumption that small changes under
the metric $\mathcal{D}$ do not change the true class of the input and
thus should not cause the classifier to predict an erroneous class.

@@

Nevertheless, such a rigorous and precise definition of the
adversary's capability, leads to well-defined measures of
adversarial robustness that are, in principle, computable.
%
For example, given a model $f(\cdot)$, one common way to define
robustness is the worst-case loss $L$ for a given perturbation budget,
\[
\mathop{\mathbb{E}}_{(x,y) \sim \mathcal{X}}\bigg[
  \max_{x' : \mathcal{D}(x,x') < \epsilon} L\big(f(x'),y\big) \bigg].
\]
Another commonly adopted definition is the average (or median)
minimum-distance of the adversarial perturbation,
\[
\mathop{\mathbb{E}}_{(x,y) \sim \mathcal{X}}\bigg[
  \min_{x' \in A_{x,y}} \mathcal{D}(x,x') \bigg],
\]
where $A_{x,y}$ depends on the definition of \emph{adversarial example},
e.g. $A_{x,y} = \{x' \mid f(x') \ne y\}$ for misclassification
or $A_{x,y} = \{x \mid f(x') = t\}$ for some target class $t$.
